\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-10-30 paper/mswp2012-proposal.tex
corrected spelling mistakes... latex does not compile at my machine due to multiline \author command???

The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system for the users. So the users are able to find out how healthy they life. \\

The project is split into different phases. This enables a useable product after a short time but the vision is a long-term development. For each phase it is necessary to find different partner in economy and politics. The partners use the platform for advertisement and for costumer relationship. So the partners have benefits too. \\

@@

When a user buys something in a shop of a partner he can register the products within an App. In the System the consummations get anonymised saved and analyzed based on a transparent score-schema. \\

The user can exchange the scores for gifts like coupons for healthy shopping by a partner. Moreover the platform can be used for rankings (which of the user live most healthy?) and lotteries. The partner can interact with the user over the platform. So they can advertise new promotions. This promotion can be used by the user for getting additional scores. \\

The goals of the platform:
\begin{itemize}
\item \textbf{Health of the User}: The peoples are getting more sensible for health-care. So they are going to live in a healthier way. The healthcare-system is very expansive. So the whole government will have a benefit from this platform and more healthier people. 
\item \textbf{Advertisment for the Partner}: For the partner the platform offers a chance to advertise their promotions. Furthermore they have the chance to spend coupons to the user. With this coupon they can interact with the costumer. So the customer loyalty is getting gain. The costumer is getting animated to buy more by partners. For this the partner has to refinance a part of the platform. 
\item \textbf{Benefits for User}: The User should get cheaper prices, when they buy some healthy things within partner stores. For example the coupons from an lottery in this platform.

>>>>

The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system to give users an easy-understandable overview on how healthy they live.\\

The project is split into different phases. This leads to the creation of a useable, rudimentary product after a short time. Nevertheless, the vision is a long-term development. For each phase it is necessary to find different partners in economy and politics. The partners use the platform for advertisement and customer relationship. So the partners have benefits too. \\

@@

When a user buys something in a shop of a partner he can register the product within an app. In the system the purchases get anonymised, saved and analyzed based on a transparent score-schema. \\

The user can exchange the scores for gifts like coupons for healthy shopping at a partners store. Moreover the platform can be used for rankings (which of the user lives most healthy?) and lotteries. Partners are able to interact with the user over the platform. So they can advertise new promotions. This promotion can be used by the user for getting additional scores. \\

The goals of the platform:
\begin{itemize}
\item \textbf{Health of the user}: People are getting more sensible for health-care. So they get forced to live in a healthier way. The healthcare-system is very expensive. So the whole government will have a benefit from this platform and more healthier people. 
\item \textbf{Advertisement for the partners}: For the partners the platform offers a chance to advertise their promotions. Furthermore they have the chance to give coupons to the users. With this coupon they can interact with the customer. One possible effect is a gain in customer loyalty. The customer is getting animated to buy more at partners stores. Therefore partners have to refinance a part of the platform.
\item \textbf{Benefits for users}: Users should be given discounts when they buy some healthy things at partners stores. This could be achieved by giving coupons to users from a lottery in the platform.
